---
title: "New-York-Evictions"
author: "Lambridge"
date: "2021/12/14"
output: html_document
---

## R Markdown

```{r}
#library a bunch of packages we may (or may not) use - install them first if not installed already. 
library(tidyverse)
library(tmap)
library(geojsonio)
library(plotly)
library(rgdal)
library(broom)
library(mapview)
library(crosstalk)
library(sf)
library(sp)
library(spdep)
library(car)
library(fs)
library(janitor)
```


# 1.load the data
```{r}
NewYorkEvictions <- read_csv(here::here("data","Evictions.csv"),
                             na = c("", "NA", "n/a"),
                             col_names = TRUE)
```

```{r}
NewYorkward <- st_read(here::here("data",
                                  "geo_export_fa9a0e50-df42-4145-8eb8-ab3c9d783141.shp")) %>%
  st_transform(.,27700)
  
```

```{r}
summary(NewYorkward)
```

```{r}
tmap_mode("view")
tm_shape(NewYorkward) +
  tm_polygons(col = NA, alpha = 0.5)

```
```{r}
Datatypelist <- NewYorkEvictions %>% 
  summarise_all(class) %>%
  pivot_longer(everything(), 
               names_to="All_variables", 
               values_to="Variable_class")

Datatypelist
```

```{r}
NewYorkEvictionsCoords <- NewYorkEvictions %>%
  na.omit()%>%
  #删除空值
  st_as_sf(., coords = c("Longitude", "Latitude"), 
                   crs = 4326) %>%
  st_transform(., 27700)
  
  
```

## Now get the location of Eviction in the City
```{r}
tmap_mode("plot")
tm_shape(NewYorkward) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(NewYorkEvictionsCoords) +
  tm_dots(col = "blue")

```
# 2Data cleaning
```{r}
library(tidyverse)

library(sf)
NewYorkEvictionsCoords <- distinct(NewYorkEvictionsCoords)
```

```{r}
Joinfun <- function(data1, data2){

output<- data1%>%
  st_join(NewYorkward,.)%>%
  add_count(boro_cd, name="eviction-borough") 

  return(output)
}
```


```{r}
NewYorkEvictionsCoords <- Joinfun(NewYorkEvictionsCoords,NewYorkward)
```

```{r}
NewYorkEvictionsCoords_groupby <- NewYorkEvictionsCoords %>% 
  group_by(.,boro_cd) %>%
  summarise("Point sum" = unique(`eviction-borough`))
```

```{r}
tm2 <- tm_shape(NewYorkEvictionsCoords_groupby)+
  tm_polygons("Point sum",
              palette="PuBu")+
  tm_legend(show=FALSE)+
  tm_layout(frame=FALSE)+
  tm_credits("(a)",position = c(0,0.85,size=1.5))

legend <- tm_shape(NewYorkEvictionsCoords_groupby) +
    tm_polygons("Point sum",
                palette="PuBu") +
    tm_scale_bar(position=c(0.2,0.04), text.size=0.6)+
    tm_compass(north=0, position=c(0.65,0.6))+
    tm_layout(legend.only = TRUE, legend.position=c(0.2,0.25),asp=0.1)+
    tm_credits("legend of New York", position=c(0.0,0.0))
t=tmap_arrange( tm2, legend, ncol=2)
t
```


```{r}
NewYorkbb = st_bbox(NewYorkEvictionsCoords_groupby,
                    crs = st_crs(NewYorkEvictionsCoords_groupby)) %>% 
  st_as_sfc()
```

```{r}
main <- tm_shape(NewYorkEvictionsCoords_groupby, bbbox = NewYorkbb) +
  tm_polygons("Point sum",
              palette = "PuBu") +
  tm_scale_bar(position = c("left", "bottom", text.size = .75)) +
  tm_layout(
    legend.position = c("right", "top"),
    legend.text.size = .75,
    legend.title.size = 1.1,
    frame = FALSE
  ) +
  tm_credits("(c)OpenstreeMap contrbutors and Airbnb", position = c(0.0, 0.0)) +
  tm_compass(type = "8star", position = c(0.06, 0.1)) +
  tm_layout(inner.margins = c(0.002, 0.002, 0.002, 0.2))
main
```
```{r}
tmap_mode("view")

tm_shape(NewYorkEvictionsCoords_groupby) + 
  tm_polygons("Point sum") 


```


```{r}
#extract the borough

Ward311 <- NewYorkward %>%
  filter(., boro_cd==311)

#Check to see that the correct borough has been pulled out
tm_shape(Ward311) +
  tm_polygons(col = NA, alpha = 0.5)
```

```{r}
#clip the data to our single borough
NewYorkEvictionsCoordsSub <- NewYorkEvictionsCoords[Ward311,]
#check that it's worked
tmap_mode("plot")
```

```{r}
tm_shape(Ward311) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(NewYorkEvictionsCoordsSub) +
  tm_dots(col = "blue")
```

```{r}
#now set a window as the borough boundary
library(spatstat)
window <- as.owin(Ward311)
plot(window)
```
```{r}
#create a sp object
NewYorkEvictionsCoordsSub<- NewYorkEvictionsCoordsSub %>%
  as(., 'Spatial')
#create a ppp object
NewYorkEvictionsCoordsSub.ppp <- ppp(x=NewYorkEvictionsCoordsSub@coords[,1],
                          y=NewYorkEvictionsCoordsSub@coords[,2],
                          window=window)
```

```{r}
NewYorkEvictionsCoordsSub.ppp %>%
  plot(.,pch=16,cex=0.5, 
       main="Blue Plaques Ward311")
```
# Point pattern analysis
```{r}
NewYorkEvictionsCoordsSub.ppp %>%
  density(., sigma=500) %>%
  plot()
```

```{r}
K <- NewYorkEvictionsCoordsSub.ppp %>%
  Kest(., correction="border") %>%
  plot()
```
 The value of K falls above the line, the New York evictions show the clustered in this ward. 

# 3.基于密度的噪声应用空间聚类：DBSCAN


```{r}
library(raster)
library(fpc)
```

```{r}
st_geometry(NewYorkward) %>% 
  st_transform(., 27700)
```

```{r}
#first extract the points from the spatial points data frame
NewYorkEvictionsCoordsSubPoints <- NewYorkEvictionsCoordsSub %>%
  coordinates(.)%>%
  as.data.frame()

#now run the dbscan analysis
db <- NewYorkEvictionsCoordsSubPoints %>%
  fpc::dbscan(.,eps = 700, MinPts = 8)

#now plot the results
plot(db, NewYorkEvictionsCoordsSubPoints, main = "DBSCAN Output", frame = F)
plot(NewYorkward$geometry, add=T)
```


6.8点模式分析总结
这是点模式分析部分的实践的结束。您已经了解了点模式分析的基础知识，该分析检查了伦敦自治市镇中蓝色斑块的分布。在这一点上，您可能希望尝试在不同的行政区（或整个城市）上运行类似的分析，并尝试使用一些输出 - 尽管您会发现，如果您尝试对那么多点运行分析，Ripley的K会很快下降）这就是您在其他上下文中或使用不同点数据时使用这些技术的方式.....
```{r}
summary(NewYorkEvictionsCoords)
```

```{r}
NewYorkEvictionsCoordsSub_NEW <- NewYorkEvictionsCoords[NewYorkward,]

tm_shape(NewYorkward) +
  tm_polygons(col = NA, alpha = 0.5) +
tm_shape(NewYorkEvictionsCoordsSub_NEW) +
  tm_dots(col = "blue")
```

```{r}
library(sf)
points_sf_Joined <- NewYorkward %>%
  st_join(NewYorkEvictionsCoordsSub_NEW)%>%
  add_count(boro_cd)%>%
  janitor::clean_names()

points_sf_Joined <- points_sf_Joined %>%
  #calculate area
  mutate(area=st_area(.))%>%
  #then density of the points per ward
  mutate(density=n/area)%>%
  #select density and some other variables 
  dplyr::select(density,boro_cd, n)
```

```{r}
points_sf_Joined<- points_sf_Joined %>%                    
  group_by(boro_cd) %>%         
  summarise(density = first(density),
          wardname= first(boro_cd),
          plaquecount= first(n))
```

```{r}
tm_shape(points_sf_Joined) +
    tm_polygons("density",
        style="jenks",
        palette="PuOr",
        midpoint=NA,
        popup.vars=c("wardname", "density"),
        title="NewYork Density")

```

```{r}
library(spdep)
```

```{r}
coordsW <- points_sf_Joined%>%
  st_centroid()%>%
  st_geometry()
  
plot(coordsW,axes=TRUE)
```

```{r}
#create a neighbours list
LWard_nb <- points_sf_Joined %>%
  poly2nb(., queen=T)
```

```{r}
summary(LWard_nb)
```

```{r}
#plot them
plot(LWard_nb, st_geometry(coordsW), col="red")
#add a map underneath
plot(points_sf_Joined$geometry, add=T)
```

```{r}
#create a spatial weights matrix from these weights
Lward.lw <- LWard_nb %>%
  nb2mat(., style="B")

sum(Lward.lw)
```

```{r}
sum(Lward.lw[,1])
```

```{r}
Lward.lw <- LWard_nb %>%
  nb2listw(., style="C")
```

```{r}
I_LWard_Global_Density <- points_sf_Joined %>%
  pull(density) %>%
  as.vector()%>%
  moran.test(., Lward.lw)

I_LWard_Global_Density
```
```{r}
C_LWard_Global_Density <- 
  points_sf_Joined %>%
  pull(density) %>%
  as.vector()%>%
  geary.test(., Lward.lw)

C_LWard_Global_Density
```

```{r}
G_LWard_Global_Density <- 
  points_sf_Joined %>%
  pull(density) %>%
  as.vector()%>%
  globalG.test(., Lward.lw)

G_LWard_Global_Density
```
```{r}
#use the localmoran function to generate I for each ward in the city

I_LWard_Local_count <- points_sf_Joined %>%
  pull(plaquecount) %>%
  as.vector()%>%
  localmoran(., Lward.lw)%>%
  as_tibble()

I_LWard_Local_Density <- points_sf_Joined %>%
  pull(density) %>%
  as.vector()%>%
  localmoran(., Lward.lw)%>%
  as_tibble()

#what does the output (the localMoran object) look like?
slice_head(I_LWard_Local_Density, n=5)
```

```{r}
points_sf_joined <- points_sf_Joined %>%
  mutate(Evictions_count_I = as.numeric(I_LWard_Local_count$Ii))%>%
  mutate(Evictions_count_Iz =as.numeric(I_LWard_Local_count$Z.Ii))%>%
  mutate(density_I =as.numeric(I_LWard_Local_Density$Ii))%>%
  mutate(density_Iz =as.numeric(I_LWard_Local_Density$Z.Ii))
```

```{r}
breaks1<-c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)
```

```{r}
library(RColorBrewer)
MoranColours<- rev(brewer.pal(8, "RdGy"))

```

```{r}
tm_shape(points_sf_joined) +
    tm_polygons("Evictions_count_Iz",
        style="fixed",
        breaks=breaks1,
        palette=MoranColours,
        midpoint=NA,
        title="Local Moran's I, Evictions in NewYork")
```

```{r}
Gi_LWard_Local_Density <- points_sf_joined %>%
  pull(density) %>%
  as.vector()%>%
  localG(., Lward.lw)

head(Gi_LWard_Local_Density)
```

```{r}
points_sf_joined <- points_sf_joined %>%
  mutate(density_G = as.numeric(Gi_LWard_Local_Density))
```

```{r}
GIColours<- rev(brewer.pal(8, "RdBu"))

#now plot on an interactive map
tm_shape(points_sf_joined) +
    tm_polygons("density_G",
        style="fixed",
        breaks=breaks1,
        palette=GIColours,
        midpoint=NA,
        title="Gi*, Ecictions in NewYork")
```

1+1